Predicting solutions for the Military Flight and Maintenance Planning problem

### 2020-09-09 R/presentations/EDAA202003/presentation.Rmd
changes to EDAA ppt

1. Problem.
2. State of the art.
1. Solving techniques.
2. Machine Learning.
2. Experiments.
3. Conclusions.

@@

### Experiments

* Number of instances: medium (1000), large (1000) and very large (1000).
* Time limit at 3600 seconds.
* We seeded instance generation for better comparison.
* CPLEX running 1 thread.

Largest instances have 60 aircraft, 90 periods, ~30 missions (4 active missions at any given time).

1. Create forecasting model based in 5000 small instances.
2. Use forecasting model to predict bounds on distance between maintenances: $\hat{\mu}_{t'-t}^{lb}$,  $\hat{\mu}_{t'-t}^{ub}$.
3. Implement the pseudo-cut:

\begin{align}
    & m_{ip} = 0 & p_{t'} - p_t < \hat{\mu}_{t'-t}^{lb} - tol \label{eq:dist_lb} \\
    & m_{ip} = 0  &  p_{t'} - p_t > \hat{\mu}_{t'-t}^{ub} + tol \label{eq:dist_ub}
\end{align}

4. Recycling.

@@

>>>>

1. Problem.
2. State of the art.
1. Solving techniques.
2. Machine Learning.
2. Results.
3. Conclusions.

@@

@@

## Communications and publications

Conferences:

* **ROADEF2018**: Maintenance planning on French military aircraft operations.
* **MOSIM2018**: Bi-objective MIP formulation for the optimization of maintenance planning on French military aircraft operations.
* **CLAIO2018**: A novel MIP formulation for the optimization problem of maintenance planning of military aircraft.
* **AFIS2018**: Planning aircraft maintenances for the French Airforce.
* **ROADEF2020**: An alternative MIP formulation for the Military Flight and Maintenance Planning problem.

Journals:

* **OR Spectrum** (published): A novel solution approach with ML-based pseudo-cuts for the Flight and Maintenance Planning problem.
* **Annals of Operations Research** (submitted): Long term planning of military aircraft flight and maintenance operations
* **European Journal of Operations Research** (to be submitted): Novel Graph-based matheuristic to solve the Flight and Maintenance Planning problem

Partnerships:

* **Dasault Aviation**: desktop software OPTIMA built, tested, deployed and validated by users.

*Estimated thesis defense: Novembre 2020.*
